---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidymrp

<!-- badges: start -->
  [![R-CMD-check](https://github.com/joekroese/tidymrp/workflows/R-CMD-check/badge.svg)](https://github.com/joekroese/tidymrp/actions)
<!-- badges: end -->

tidymrp makes it easy to run multilevel regression and poststratification (MRP) analyses in R. It fits neatly into the tidyverse and can be used with a range of modelling packages from frequentist to Bayesian.

The focus of the package is on providing functions useful for MRP workflows including creating poststratification frames, poststratifying and visualising MRP results.

## Getting Started

### Installation

Install the latest development version from GitHub:

```{r eval = FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("joekroese/tidymrp")
```
