---
title: "MRP"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MRP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
library(tidymrp)
library(magrittr)
library(brms)
```

```{r}
# options(mc.cores = parallel::detectCores())
```

## Get data

```{r}
data(example_survey)
data(example_census)
```

## Build model

We believe that age influences the value of non_negative_response. This is a continuous variable. The easiest way to integrate it is by discretising it.

```{r}
example_survey <- example_survey %>%
  mutate(age_group = case_when(
    age %in% 16:24 ~ "16_to_24",
    age %in% 25:34 ~ "25_to_34",
    age %in% 35:44 ~ "35_to_44",
    age %in% 45:54 ~ "45_to_54",
    age %in% 55:64 ~ "55_to_64",
    age >= 65 ~ "65_plus")
  )
```

```{r}
non_negative_response_model_1 <- example_survey %>%
  head(1000) %>%
  brms::brm(
    bf(non_negative_response ~ 1 + (1 | age_group),
       shape ~ 1 + (1 | age_group)),
    family = Gamma(),
    data = .,
    chains = parallel::detectCores(),
    iter = 200, # 200 is normally enough to get the idea
    file = "models/non_negative_response_model_1"
  )
```

## Prepare poststratification

We need to know how many people are in each strata. To do that, we turn the census into a poststratification frame. This means grouping along the variables in the model to make stratas. We then summing the number of people in each strata.

<!-- Turn the census into a poststratification frame by grouping along the categorical variables used in the model and summing all the people in those stratas. -->

```{r}
poststratification_frame <- example_census %>%
  create_poststratification_frame(strata_variables = c(age_group, region),
                                  weight_column = n)
```

## Get estimates

```{r}
poststratified_estimates <- poststratify(model = non_negative_response_model_1,
                                         poststratification_frame = poststratification_frame,
                                         estimates_by = region)
poststratified_estimates
```
